\systemEnding: A Wake/Sleep Algorithm for Developing Domain Expertise

### 2019-05-02 archive.tex
deep program learning
title

\begin{document}

@@

\begin{figure}\centering
  \includegraphics[width = \textwidth]{figures/deepLogo_may1}
  \includegraphics[width = \textwidth]{figures/deepList_may1}
  \caption{Model solves tasks (left; top, task is to draw an image. bottom, task is input/output mapping) by writing programs (right column) where these programs invoke explicit declarative knowledge in the form of library routines (middle) jointly learned w/ the solutions. Library code can call each other (arrows), forming a layered network of domain-specific concepts. %% Fantasies (below library) are tasks sampled by randomly combining code from library. Fantasies are used to train a neural net to help search for programs.
  }\label{exampleDSL}
\end{figure}

@@

\subsection{Analyzing \system across domains}\label{quantitative}
To evaluate the relative importance of library learning and recognition
model training, we evaluate on held-out testing tasks for each of our
domains, measuring both how many tasks are solved and how long it
takes to solve them across successive wake/sleep iterations
(Fig.~\ref{learningCurves}).  We always solve more held-out tasks --
and generally solve them in less time -- with both components
combined, suggesting a synergy between these forms of declarative and procedural knowledge.
Examining the libraries learned with and without
recognition models reveals a difference in the typical \emph{depth}
of learned subroutines, and this average depth correlates
with the number of solved testing tasks ($r=0.71$, $p < 10^{-8}$).
In contrast, the correlation between the \emph{number} of learned subroutines and number of solved tasks is weaker and not statistically significant ($r=0.20$, $p > 0.05$),
suggesting that the recognition model bootstraps
``better'' libraries, where ``better'' is at least partly explained by the depth
of the learned representation. Figure~\ref{depthMontage} shows typical `deep' libraries learned by
\system and contrasts this depth with \% solved tasks, both with and without the recognition model.
\begin{figure}
  \begin{tabular}{ccc}
    \begin{tabular}{c}
      \includegraphics[width = 5cm]{figures/learningCurves/text_hits.png}\\
      \includegraphics[width = 5cm]{figures/learningCurves/text_time.png}
    \end{tabular}&

@@

\begin{figure}
  \includegraphics[width = \textwidth]{deepMontage.pdf}
  \caption{Top: Learned libraries diagrammed as networks. Arrows point from a learned concept to all other concepts that use it. Bottom: Deeper networks solve more testing tasks, both as measured by average depth (left) and maximum depth (middle), while total library size is more weakly associated with solving tasks (right). Full model (stars on scatterplots) learns deeper libraries than no-recognition-model ablation (triangles on scatterplots). Each scatter plot point run with a different random seed.}\label{depthMontage}
\end{figure}

>>>>

\title{\systemEnding: A Wake/Sleep Algorithm for Developing Domain Expertise}
\date{}
\begin{document}
\maketitle{}

@@

\begin{figure}\centering
  \includegraphics[width = \textwidth]{figures/deepLogo_may2.pdf}\vspace{2.5cm}
  \includegraphics[width = \textwidth]{figures/deepList_may2.pdf}
  \caption{Model solves tasks (left; top, task is to draw an image. bottom, task is input/output mapping) by writing programs (right column) where these programs invoke explicit declarative knowledge in the form of library routines (middle) jointly learned w/ the solutions. Library code can call each other (arrows), forming a layered network of domain-specific concepts. %% Fantasies (below library) are tasks sampled by randomly combining code from library. Fantasies are used to train a neural net to help search for programs.
  }\label{exampleDSL}
\end{figure}

@@

\subsection{Analyzing \system across domains}\label{quantitative}
To evaluate the relative importance of library learning and recognition
model training, we evaluate on held-out testing tasks for each of our
domains, measuring both how many tasks are solved and how long it
takes to solve them across successive wake/sleep iterations
(Fig.~\ref{learningCurves}).  We always solve more held-out tasks --
and generally solve them in less time -- with both components
combined, suggesting a synergy between these forms of declarative and procedural knowledge.
Examining the libraries learned with and without
recognition models reveals a difference in the typical \emph{depth}
of learned subroutines, and this average depth correlates
with the number of solved testing tasks ($r=0.71$, $p < 10^{-8}$).
In contrast, the correlation between the \emph{number} of learned subroutines and number of solved tasks is weaker ($r=0.20$, $p > 0.05$), although, within each domain, the recognition model still leads to bigger libraries.
These results suggest that the recognition model bootstraps
``better'' libraries, where ``better'' is largely explained by the depth
of the learned representation. Figure~\ref{depthMontage} shows typical `deep' libraries learned by
\system and contrasts this depth with \% solved tasks, both with and without the recognition model.
\begin{figure}
  \begin{tabular}{ccc}
    \begin{tabular}{c}
      \includegraphics[width = 5cm]{figures/learningCurves/text_hits.png}\\
      \includegraphics[width = 5cm]{figures/learningCurves/text_time.png}
    \end{tabular}&

@@

\begin{figure}
  \includegraphics[width = \textwidth]{deepMontage.pdf}
  \caption{Top: Learned libraries diagrammed as networks. Arrows point from a learned concept to all other concepts that use it. Bottom: Deeper networks solve more testing tasks, both as measured by average depth (left) and maximum depth (middle). Total library size is more also associated with solving tasks (right), but across domains the association is weaker. Full model (stars on scatterplots) learns bigger and deeper libraries than no-recognition-model ablation (triangles on scatterplots). Each scatter plot point run with a different random seed.}\label{depthMontage}
\end{figure}
